%% Compile with: pdflatex resume_faangpath.tex  (run twice)
    \documentclass{resume}
    \begin{document}
    
    %% HEADER
    \resumeheader
      {Romesh Jain}
      {Software Engineer · React.js · Next.js · React Native · Node.js · AI-Augmented Full-Stack Development}
      {+91-9516949156}
      {romeshjainofficial@gmail.com}
      {https://linkedin.com/in/romeshjain/}
      {https://github.com/romeshjainn}
      {https://romesh.online/}
    \vspace{1pt}

    %% TECHNICAL SKILLS
    \section{Technical Skills}
    
    \begin{tabular}{@{} p{2.0cm} p{14.1cm} @{}}
      \skillrow{Languages}{JavaScript (ES6+), TypeScript}
      \skillrow{Frontend}{React.js, Next.js (SSR/SSG/ISR), Redux Toolkit, Tailwind CSS, NativeWind, HTML5, CSS3}
      \skillrow{Mobile}{React Native, Ionic Capacitor, Android Deployment, Biometric Auth, Offline Caching}
      \skillrow{Backend}{Node.js, Express.js, REST APIs, JWT, Firebase (Auth, FCM, Firestore), WebSockets}
      \skillrow{Databases}{MongoDB, PostgreSQL, Firestore, Redis, Supabase}
      \skillrow{Integrations}{Stripe, Google Maps API, Calendly, OneSignal, Social Login (OAuth 2.0)}
      \skillrow{Tools \& Ops}{Git, GitHub, Postman, Vercel, Netlify, Figma, CI/CD, Agile/Scrum}
      \skillrow{AI \& Dev}{Claude, GitHub Copilot, Ollama (Local LLMs), Prompt Engineering, AI-assisted workflows}
    \end{tabular}
    
    %% PROFESSIONAL EXPERIENCE
    \section{Professional Experience}
    
    \companyheader{DigiMonk Technologies}{https://digimonk.in}{Gwalior, India}
    
    \roleentry{Software Engineer}{Jan 2026 -- Present}
    \begin{itemize}
      \item Architected multi-tier RBAC admin panels (super-admin, clinician, content-admin) across 3 production apps; used AI-assisted code generation (Copilot + Claude) to produce \textbf{\textasciitilde70\% of scaffold code}, accelerating feature delivery.
      \item Built real-time chat + push notification system via WebSockets and Firebase FCM, improving response times and boosting user engagement across apps.
      \item Improved Lighthouse performance scores through Next.js code-splitting, lazy loading, and image optimisation on high-traffic dashboards.
    \end{itemize}
    
    \vspace{1pt}

    \roleentry{Associate Software Engineer}{Dec 2024 -- Jan 2026}
    \begin{itemize}
      \item Engineered a shared React.js / React Native component library adopted across 4+ apps, eliminating code duplication and accelerating sprint delivery.
      \item Delivered data-heavy dashboards with SSR pagination, debounced search, and infinite scroll -- handling large datasets with zero observable lag.
      \item Integrated Stripe, Google Maps API, Firebase Auth, and OneSignal across 5 projects with zero post-launch regressions.
    \end{itemize}
    
    \vspace{1pt}

    \roleentry{Graduate Trainee}{Apr 2024 -- Dec 2024}
    \begin{itemize}
      \item Contributed production-ready components from sprint one; reduced UI bug backlog through systematic layout audits and cross-browser testing; onboarded into Git, CI/CD, and PR review workflows within the first month.
    \end{itemize}
    
    \vspace{1pt}

    \companyheader{InOffice Labs}{}{Remote}
    
    \roleentry{Web Developer Intern}{Oct 2023 -- Mar 2024}
    \begin{itemize}
      \item Built pixel-perfect, reusable React.js components from Figma mockups; adopted product-wide with no rework required.
    \end{itemize}
    
    %% KEY PROJECTS
    \section{Key Projects}
    
    \projectentry{PROTOCOL -- Health-Tech Diagnostics Platform}{Next.js · Redux · Stripe · Calendly API · REST APIs}
    \begin{itemize}
      \item AI-driven patient dashboards with biomarker scores; integrated Stripe subscriptions and Calendly booking, reducing manual operations overhead.
    \end{itemize}
    
    \vspace{1pt}

    \projectentry{AI-Powered LMS [\href{https://github.com/romeshjainn/lms-app}{\underline{GitHub}}]}{React Native · Node.js · LLM Integration · AI-Augmented Dev}
    \begin{itemize}
      \item Fully functional LMS featuring biometric auth, AI learning assistant, offline caching, and push notifications -- \textbf{100\% AI-assisted} (Claude + Copilot) in \textbf{3 days} alongside a full-time job.
    \end{itemize}
    
    \vspace{1pt}

    \projectentry{SAHEL -- Service Booking Platform}{Next.js · React Native · Redux · Firebase · WebSockets · Node.js}
    \begin{itemize}
      \item Cross-platform app (mobile + web admin) with real-time technician dispatch, multi-tier RBAC, and FCM notifications segmented by city and schedule.
    \end{itemize}
    
    \vspace{1pt}

    \projectentry{SuprFind -- Local Business Listing Platform}{Next.js · Redux · Google Maps API}
    \begin{itemize}
      \item Advertiser and admin panels with Google Maps geo-search, pin-drop, and analytics tracking impressions, visits, and calls.
    \end{itemize}
    
    %% ACHIEVEMENTS & CERTIFICATIONS
    \section{Achievements \& Certifications}
    
    \begin{itemize}
      \item Anthropic Certifications: \href{https://verify.skilljar.com/c/738qqbw7mdzg}{\underline{Claude 101}}, \href{https://verify.skilljar.com/c/y7sjp6gizmbk}{\underline{Claude Code in Action}}, \href{https://verify.skilljar.com/c/yhi5c9jiyomj}{\underline{Introduction to Agent Skills}} \enspace|\enspace Be10X: \href{https://certx.in/certificate/0270772f-3809-4400-b29b-1e1c61cd09971132989}{\underline{AI Tools Workshop}}
      \item Promoted Trainee $\to$ Associate $\to$ Software Engineer in \textbf{21 months} -- fastest in the team, driven by consistent delivery quality.
      \item Velotio Weekly LinkedIn Quiz Winner -- recognised among top respondents for technical accuracy.
    \end{itemize}
    
    %% EDUCATION
    \section{Education}
    
    \eduentry
      {Bachelor of Computer Applications (BCA)}
      {Makhanlal Chaturvedi University, Gwalior}
      {Jun 2020 -- Jun 2023}
      {CGPA: 7.67/10.0 \quad|\quad Data Structures \& Algorithms, Operating Systems, Software Engineering}
    
    \end{document}